%-------------------------
% Resume in Latex
% Author : Harshibar
% Based off of: https://github.com/jakeryang/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
% only for pdflatex
% \input{glyphtounicode}

% fontawesome
\usepackage{fontawesome5}

% fixed width
\usepackage[scale=0.90,lf]{FiraMono}

% light-grey
\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\DeclareRobustCommand{\ebseries}{\fontseries{eb}\selectfont}
\DeclareTextFontCommand{\texteb}{\ebseries}

% custom underilne
\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}


% custom font: helvetica-style
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault} 
%% Only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting - serif
% \titleformat{\section}{
%   \vspace{2pt} \scshape \raggedright\large % header section
% }{}{0em}{}[\color{black} \titlerule \vspace{-5pt}]

% TODO EBSERIES
% sans serif sections
\titleformat {\section}{
    \bfseries \vspace{2pt} \raggedright \large % header section
}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-4pt}]

% only for pdflatex
% Ensure that generate pdf is machine readable/ATS parsable
% \pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\ % top row of resume entry
      \textit{#3} & {\color{dark-grey} \small #4}\\ % second row of resume entry
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\color{dark-grey}} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% CHANGED default leftmargin  0.15 in
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\color{text-grey}

%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Haile Asaye} \\ \vspace{3pt}
    {\large Full-Stack Engineer } \\ \vspace{5pt}
    \small 
    \faPhone* \texttt{+251972671351} \hspace{1pt} $|$
    \hspace{1pt} \faEnvelope \hspace{2pt} \texttt{haileasaye51@gmail.com} \hspace{1pt} $|$ 
    \hspace{1pt} \faGithub \hspace{2pt} \texttt{github.com/ispastro} \hspace{1pt} $|$
    \hspace{1pt} \faGlobe \hspace{2pt}\texttt{haileasaye.me}
\end{center}



%-----------EXPERIENCE-----------
\section{EXPERIENCE}
\resumeSubHeadingListStart

  \resumeSubheading
      {Million Trading PLC}{Nov 2025 -- Mar 2026}
      {Full Stack Developer}{Addis Ababa, Ethiopia}
      \resumeItemListStart
        \resumeItem{Built high-performance interfaces using \textbf{ Next.js, and TypeScript}.}
        \resumeItem{Optimized rendering performance via \textbf{memoization, lazy loading, and efficient state management}.}
        \resumeItem{Managed asynchronous data flows and complex UI states in production environments.}
                \resumeItem{built  realtime backend services , tested optimized and deployed to the GCP.}

        \resumeItem{Improved accessibility , responsiveness, and cross-browser compatibility.}
                \resumeItem{Integrated the Web App with the Telegram bot.}

      \resumeItemListEnd

  \resumeSubheading
      {GA Soft Solution(GA Engineering Group)}{Sept 2025-- Jan 2026}
      {Web Developer intern}{Addis Ababa, Ethiopia}
      \resumeItemListStart
        
        \resumeItem{Implemented asynchronous request handling and optimized API performance.}
        \resumeItem{Designed component based modular front end architecture .}
        \resumeItem{Integrated front end  with backend services using scalable data-fetching patterns.}
        \resumeItem{Improved system reliability through structured logging, debugging, and error handling.}
      \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{PROJECTS}
\resumeSubHeadingListStart

    \resumeProjectHeading{\textbf{SkillSwap} $|$ \href{https://github.com/ispastro/skill-swap.git}{\myuline{Code}}}{}
      \resumeItemListStart
        \resumeItem{Built micro-service AI powered   full-stack marketplace using \textbf{Next.js, Node.js, FastAPI and Express}.}
        \resumeItem{Designed REST APIs with real-time communication and efficient data synchronization.}
        \resumeItem{Structured backend logic for scalable feature extension and maintainability.}
      \resumeItemListEnd

    \resumeProjectHeading{\textbf{Mindo (PWA)} $|$ \href{https://mindo-4u.vercel.app}{\myuline{Live}} $|$ 
    \href{https://github.com/ispastro/mindo-4g.git}{\myuline{Code}}}{}
      \resumeItemListStart
        \resumeItem{Developed an offline-first Progressive Web App with optimized caching strategies.}
        \resumeItem{Improved frontend performance through lazy loading and efficient asset delivery.}
      \resumeItemListEnd

    \resumeProjectHeading{\textbf{InterviewMe-AI} $|$ \href{https://interviewme-ai.vercel.app/}{\myuline{Live}} $|$
    \href{https://github.com/ispastro/InterviewAI.git}{\myuline{Code}}}{}
      \resumeItemListStart
        \resumeItem{Built AI powered Interview practice platform with scalable backend  pipelines using \textbf{Python(FastAPI)} for data processing and dynamic evaluation.}
        \resumeItem{Designed modular system architecture for scalable feature integration.}
      \resumeItemListEnd

    \resumeProjectHeading{\textbf{PilotAlert} $|$ \href{https://github.com/ispastro/pilot_ping}{\myuline{Code}}}{}
      \resumeItemListStart
        \resumeItem{Developed an automation system with scheduled tasks and event-driven notifications.}
        \resumeItem{Implemented background processing and reliable task execution workflows.}
      \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{EDUCATION}
\resumeSubHeadingListStart
  \resumeSubheading
      {Addis Ababa University} {}
      {BSc in Computer Information Systems}{Addis Ababa, Ethiopia}
\resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{SKILLS}
\begin{itemize}[leftmargin=0in, label={}]
\small{\item{

\textbf{Languages}: Python, JavaScript, TypeScript, SQL \\[6pt]

\textbf{Frontend}: React.js, Next.js, Performance Optimization, Accessibility, Telegram Mini APPs \\[6pt]

\textbf{Backend}: FastAPI, , Express.js, Node.js, REST APIs, Async Processing \\[6pt], Scalability 

\textbf{Databases}: PostgreSQL (schema design, indexing), , MongoDB ,\\[6pt]

\textbf{System Design}: API Design, Scalable Architecture, Data Modeling \\[6pt]

\textbf{DevOps}: Docker, CI/CD, GitHub Actions \\[6pt]

\textbf{Cloud}: AWS, GCP, Vercel , Heroku\\[6pt]

\textbf{Additional}: Supabase, WebSockets, Event-Driven Systems \\[6pt]

\textbf{Tools}: Git, GitHub, Postman \\[6pt]

\textbf{Practices}: Clean Code, Testing, Debugging, Code Review

}}
\end{itemize}

\end{document}